Final Report: Measles risk assessment, modelling, and benefit--cost analyses for New Zealand

### 2015-09-25 draftfinalreport_v4.Rnw
fixup label to autoref

Our estimates of the costs of the measles outbreaks in New Zealand suggest that measles management costs per case in New Zealand is high. We used the mean values per case in the absence of alternative data and used all available data. The exact costs will vary, however, our benefit--cost analyses suggest that in all cases catch up immunisation schemes will be financially beneficial for New Zealand (see \autoref{table:cost20} and \autoref{table:cost50}). Additional vaccination beyond the \Sexpr{vacc_reqd_percent}\% of currently na\"{\i}ve population we estimate are required to be vaccinated for $R_0 < 1$ decrease the cost effectiveness of an immunisation program. This is because large outbreaks are avoided once $R_0 < 1$. In the scenario we modelled with 50\% of the currently na\"{\i}ve population immunised, costs exceed benefits at \$\Sexpr{break_even_vacc_cost50} per immunised person \label{table:cost50pc}. There may be other benefits we have not accounted for in our analyses for additional vaccination. These additional benefits may include reducing the possibility of spatial heterogeneity and future benefits beyond the ten year period we modelled.

>>>>

Our estimates of the costs of the measles outbreaks in New Zealand suggest that measles management costs per case in New Zealand is high. We used the mean values per case in the absence of alternative data and used all available data. The exact costs will vary, however, our benefit--cost analyses suggest that in all cases catch up immunisation schemes will be financially beneficial for New Zealand (see \autoref{table:cost20} and \autoref{table:cost50}). Additional vaccination beyond the \Sexpr{vacc_reqd_percent}\% of currently na\"{\i}ve population we estimate are required to be vaccinated for $R_0 < 1$ decrease the cost effectiveness of an immunisation program. This is because large outbreaks are avoided once $R_0 < 1$. In the scenario we modelled with 50\% of the currently na\"{\i}ve population immunised, costs exceed benefits at \$\Sexpr{break_even_vacc_cost50} per immunised person \autoref{table:cost50pc}. There may be other benefits we have not accounted for in our analyses for additional vaccination. These additional benefits may include reducing the possibility of spatial heterogeneity and future benefits beyond the ten year period we modelled.
